### 2017-04-04 paper/modes.tex
comments on sec2

Forking OS processes to run test jobs is a common feature of build
systems as to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
Ant), this amounts to spawning one JVM instance (per process) per CPU,
on a machine with potentially many virtual CPUs, and aggregating
corresponding results when jobs finish.  Note that forking can only be
combined with configuration \SeqClassParMeth{} (see
Section~\ref{sec:frameworks}) as Maven only accepts one test class at
a time per forked process.\Mar{$\leftarrow$Are you sure about this?
  It seems silly.  Maybe, the rationale is to ``keep design simple''.}
To attenuate the non-trivial cost of spawning new processes and JVMs on
every test class, Maven offers an option to reuse the
JVM.\Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
  configuracao abaixo?}

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseFork},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <parallel>methods</parallel>
        <threadCount>5</threadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Configuration \ForkParMeth{} on Maven.}
\end{figure}

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
With this configuration, Maven~---~through its test plugin
Surefire~\cite{maven-surefire-plugin}~---~forks one JVM per core
(\CodeIn{forkCount} parameter) and uses five threads
(\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
parameter) within each forked JVM.

>>>>

Forking OS processes to run test jobs is a common feature of build
systems as to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
Ant), this amounts to spawning one JVM instance (per process) per CPU,
on a machine with potentially many virtual CPUs, and aggregating
corresponding results when jobs finish.  Note that forking can only be
combined with configuration \SeqClassParMeth{} (see
Section~\ref{sec:frameworks}) as Maven only accepts one test class at
a time per forked process.\Mar{$\leftarrow$Are you sure about this?
  It seems silly.  Maybe, the rationale is to ``keep design
  simple''.}\Jbc{I'm sure. in addition to keep design simple, I feel
  like this was initially conceived to run tests in isolation}
To attenuate the non-trivial cost of spawning new processes and JVMs on
every test class, Maven offers an option to reuse the
JVM.\Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
  configuracao abaixo?}\Jbc{added...}

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={parallel, threadCount, perCoreThreadCount,
    forkCount, reuseForks},
    deletekeywords={true}
}
\begin{lstlisting}
<plugin>
    <groupId>org.apache.maven.plugins</groupId>
    <artifactId>maven-surefire-plugin</artifactId>
    <configuration>
        <forkCount>1C</forkCount>
        <reuseForks>true</reuseForks>
        <parallel>methods</parallel>
        <threadCount>5</threadCount>
    </configuration>
</plugin>
\end{lstlisting}
    \caption{\label{fig:surefire} Configuration \ForkParMeth{} on Maven.}
\end{figure}

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
With this configuration, Maven~---~through its test plugin
Surefire~\cite{maven-surefire-plugin}~---~forks one JVM per core
(\CodeIn{forkCount} parameter) and uses five threads
(\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
parameter) within each forked JVM. After the execution of a test
class, Maven reuses the forked JVM for the next execution
(\CodeIn{reuseFork} parameter).
